---
title: "WFA_Analysis USDCHF - Turtle System "
author: "RJ Kumar"
date: "03/06/2017"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Walk Forward Report

This markdown document will generate a walk forward analysis report for a symbol, it will test optimization via net trading PL and the ratio of profit to maximum draw down.

```{r strategy setup, message=FALSE, warning=FALSE, include=FALSE}
# Load Quantstrat and required packages
require(quantstrat)
require(doMC)

# Set the system time to UTC
Sys.setenv(TZ="UTC")

# Get DMA include ile with parameters and Functions
source(paste(getwd(),"/TurtleInclude.R",sep=""))

# Strategy specific variables
riskpct <- 0.02 # percentage of equity to risk 
risk    <- 1

# Paramset Variables
breakoutPset  <- seq(20, 120, by = 10)
stopPset      <- seq(20, 120, by = 10)
atrMultPset   <- seq(3, 10, by = 1)

# StartDate, Training and Testing Lengths in Years
startDate <- "2000" # You must edit the getCurrData file to match this
trainingLength <- 5
testingLength <- 1

 # Get all symbols, uncomment what you need
 # source(paste(getwd(),"/GetCommData.R",sep=""))
  source(paste(getwd(),"/GetCurrData.R",sep=""))
 # source(paste(getwd(),"/GetEqData.R",sep=""))

 # Change symbol variable here if needed
 symbol <- "USDCHF"

 # Change the end dates if you need to so WFA runs without error
 endDate <- "2016"
 assign(symbol,get(symbol)[paste('/',endDate,sep = "")])
 
 # Register the cores for parralel procssing
 registerDoMC(cores=detectCores())
```

## Floating Analysis Window
### Max Trading PL Testing Summary Chart

```{r PL floating window, echo=FALSE, message=FALSE, warning=FALSE}
# Initialize the portfolio, account and orders. Starting equity and assuming data post 1995.

rm.strat(portfolio.st, silent = FALSE)
rm.strat(account.st, silent = FALSE)

initPortf(portfolio.st, symbols = symbol)
initAcct(account.st, portfolios = portfolio.st, initEq = initEq)
initOrders(portfolio = portfolio.st)

# Define the strategy with a position limit to prevent multiple trades in a direction
for (sym in symbol){
  addPosLimit(portfolio = portfolio.st, sym, timestamp="2000-01-01", maxpos=100, 
              longlevels = 1, minpos=-100, shortlevels = 1)
}

load.strategy("Turtle")

enable.rule(strat,type = "chain",label = "StopLONG")
enable.rule(strat,type = "chain",label = "StopSHORT")

# Register the cores for parralel processing
registerDoMC(cores=detectCores())

# Now apply the walk forward analysis over the parameter sets for optimization
results <- walk.forward(strategy.st = strat, paramset.label = 'Turtle_OPT', 
                        portfolio.st = portfolio.st,
                        account.st = account.st, period = 'years',
                        k.training = trainingLength,
                        k.testing = testingLength, nsamples = 0, 
                        obj.args = list(x = quote(tradeStats.list$Net.Trading.PL)),
                        audit.prefix = 'wfa', anchored=FALSE, verbose=FALSE
                        )

# Update the portfolio
updatePortf(Portfolio = portfolio.st)                                     
updateAcct(name = account.st)
updateEndEq(account.st)

#chart the position
chart.Posn(Portfolio = portfolio.st, Symbol = symbol)          # Chart the position


```

### Analysis Charts: Max Trading PL

```{r PL float graphs, echo=FALSE, message=FALSE, warning=FALSE}
# Code to chart the training periods and combined testing portfolio
n <- 1 # Set a counter

# Loop to print training perods, file names calculated from inputs 
while(n <= as.numeric(endDate)-(as.numeric(startDate)+trainingLength-1)){
  chartForwardTraining(list.files(pattern=glob2rx(paste("wfa.",symbol,".",as.numeric(startDate)+(n-1), "*", (as.numeric(startDate) + trainingLength) + (n - 2), "*.RData", sep = ""))))
  n <- n + testingLength
}

# Chart Testing Data
chartFor("wfa.results.RData")
```

### Maximum Ratio of Profit to Maximum Drawdown Testing Summary Chart

```{r profit to draw floating, echo=FALSE, message=FALSE, warning=FALSE}
# If run previously, run this code from here down
rm.strat(portfolio.st, silent = FALSE)
rm.strat(account.st, silent = FALSE)

# Initialize the portfolio, account and orders. Starting equity.
initPortf(portfolio.st, symbols = symbol)
initAcct(account.st, portfolios = portfolio.st, initEq = initEq)
initOrders(portfolio = portfolio.st)

# Define the strategy with a position limit to prevent multiple trades in a direction
for (sym in symbol){
  addPosLimit(portfolio = portfolio.st, sym, timestamp="2000-01-01", maxpos=100, 
              longlevels = 1, minpos=-100, shortlevels = 1)
}

load.strategy("Turtle")

enable.rule(strat,type = "chain",label = "StopLONG")
enable.rule(strat,type = "chain",label = "StopSHORT")

# Register the cores for parralel procssing
registerDoMC(cores=detectCores())

# Now apply the walk forward analysis over the parameter sets for optimization
results <- walk.forward(strategy.st=strat, paramset.label='Turtle_OPT', portfolio.st=portfolio.st,
                        account.st=account.st, period='years', k.training=trainingLength, k.testing=testingLength,
                        nsamples=0, obj.args = list(x = quote(tradeStats.list$Profit.To.Max.Draw)),
                        audit.prefix='wfa.p2d', anchored=FALSE, verbose=FALSE
                        )

# Update the portfolio
updatePortf(Portfolio = portfolio.st)                                     
updateAcct(name = account.st)
updateEndEq(account.st)

#chart the position
chart.Posn(Portfolio = portfolio.st, Symbol = symbol)          # Chart the position
```

### Analysis Charts: Maximum Ratio of Profit to Maximum Drawdown

```{r profit to draw floating graphs, echo=FALSE, message=FALSE, warning=FALSE}
# Code to chart the training periods and combined testing portfolio
n <- 1 # Set a counter

# Loop to print training perods, file names calculated from inputs 
while(n <= as.numeric(endDate)-(as.numeric(startDate)+trainingLength-1)){
  chartForwardTraining(list.files(pattern=glob2rx(paste("wfa.p2d.",symbol,".",as.numeric(startDate)+(n-1), "*", (as.numeric(startDate) + trainingLength) + (n - 2), "*.RData", sep = ""))))
  n <- n + testingLength
}

# Chart Testing Data
chartFor("wfa.p2d.results.RData")
```

## Anchored Analysis Window
### Max Trading PL Testing Summary Chart

```{r PL anchored, echo=FALSE, message=FALSE, warning=FALSE}
# Initialize the portfolio, account and orders. Starting equity and assuming data post 1995.

rm.strat(portfolio.st, silent = FALSE)
rm.strat(account.st, silent = FALSE)

initPortf(portfolio.st, symbols = symbol)
initAcct(account.st, portfolios = portfolio.st, initEq = initEq)
initOrders(portfolio = portfolio.st)

# Define the strategy with a position limit to prevent multiple trades in a direction
for (sym in symbol){
  addPosLimit(portfolio = portfolio.st, sym, timestamp="2000-01-01", maxpos=100, 
              longlevels = 1, minpos=-100, shortlevels = 1)
}

load.strategy("Turtle")

enable.rule(strat,type = "chain",label = "StopLONG")
enable.rule(strat,type = "chain",label = "StopSHORT")

# Register the cores for parralel processing
registerDoMC(cores=detectCores())

# Now apply the walk forward analysis over the parameter sets for optimization
results <- walk.forward(strategy.st=strat, paramset.label='Turtle_OPT', 
                        portfolio.st=portfolio.st,
                        account.st=account.st, period='years', k.training=trainingLength,
                        k.testing=testingLength, nsamples=0, 
                        obj.args = list(x = quote(tradeStats.list$Net.Trading.PL)),
                        audit.prefix='wfa.anc', anchored=TRUE, verbose=FALSE
                        )

# Update the portfolio
updatePortf(Portfolio = portfolio.st)                                     
updateAcct(name = account.st)
updateEndEq(account.st)

#chart the position
chart.Posn(Portfolio = portfolio.st, Symbol = symbol)          # Chart the position
```

### Analysis Charts: Max Trading PL

```{r PL anchored graphs, echo=FALSE, message=FALSE, warning=FALSE}
# Code to chart the training periods and combined testing portfolio
n <- 1 # Set a counter

# Loop to print training perods, file names calculated from inputs 
while(n <= as.numeric(endDate)-(as.numeric(startDate)+trainingLength-1)){
  chartForwardTraining(list.files(pattern=glob2rx(paste("wfa.anc.",symbol,".",as.numeric(startDate), "*", (as.numeric(startDate) + trainingLength) + (n - 2), "*.RData", sep = ""))))
  n <- n + testingLength
}

# Chart Testing Data
chartFor("wfa.anc.results.RData")
```

### Maximum Ratio of Profit to Maximum Drawdown Testing Summary Chart

```{r profit to draw anchored, echo=FALSE, message=FALSE, warning=FALSE}
# If run previously, run this code from here down
rm.strat(portfolio.st, silent = FALSE)
rm.strat(account.st, silent = FALSE)

# Initialize the portfolio, account and orders. Starting equity and assuming data post 1995.
initPortf(portfolio.st, symbols = symbol)
initAcct(account.st, portfolios = portfolio.st, initEq = initEq)
initOrders(portfolio = portfolio.st)

# Define the strategy with a position limit to prevent multiple trades in a direction
for (sym in symbol){
  addPosLimit(portfolio = portfolio.st, sym, timestamp="2000-01-01", maxpos=100, 
              longlevels = 1, minpos=-100, shortlevels = 1)
}

load.strategy("Turtle")

enable.rule(strat,type = "chain",label = "StopLONG")
enable.rule(strat,type = "chain",label = "StopSHORT")

# Register the cores for parralel procssing
registerDoMC(cores=detectCores())

# Now apply the walk forward analysis over the parameter sets for optimization
results <- walk.forward(strategy.st=strat, paramset.label='Turtle_OPT', portfolio.st=portfolio.st,
                        account.st=account.st, period='years', k.training=trainingLength, k.testing=testingLength,
                        nsamples=0, obj.args = list(x = quote(tradeStats.list$Profit.To.Max.Draw)),
                        audit.prefix='wfa.p2danc', anchored=TRUE, verbose=FALSE
                        )

# Update the portfolio
updatePortf(Portfolio = portfolio.st)                                     
updateAcct(name = account.st)
updateEndEq(account.st)

#chart the position
chart.Posn(Portfolio = portfolio.st, Symbol = symbol)          # Chart the position
```

### Analysis Charts: Maximum Ratio of Profit to Maximum Drawdown

```{r profit to draw anchored graphs, echo=FALSE, message=FALSE, warning=FALSE}
# Code to chart the training periods and combined testing portfolio
n <- 1 # Set a counter

# Loop to print training perods, file names calculated from inputs 
while(n <= as.numeric(endDate)-(as.numeric(startDate)+trainingLength-1)){
  chartForwardTraining(list.files(pattern=glob2rx(paste("wfa.p2danc.",symbol,".",as.numeric(startDate), "*", (as.numeric(startDate) + trainingLength) + (n - 2), "*.RData", sep = ""))))
  n <- n + testingLength
}

# Chart Testing Data
chartFor("wfa.p2danc.results.RData")
```
